---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# visualidentity

The goal of visualidentity is to build package documentation using personnalized templates.

## Installation

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("ThinkR-open/visualidentity")
```


## Examples
### Build a book from vignettes inside a package

You can use `create_book()` using your own template basis. By default, it uses {bookdown} site template. You can use it to build your own.

```{r, eval=FALSE}
template <- system.file("rstudio/templates/project/resources", package = "bookdown")
create_book(path = "inst/report", clean = TRUE,
            template = template)
```

Help users find your book with function `open_guide_function()`. This adds function `open_guide()` inside your package that will open the userguide (in HTML or PDF) on demand.

```{r, eval=FALSE}
open_guide_function(path = "inst/report")
```

### Build a pkgdown site inside a package

You can use `build_pkgdown()` using your own template basis. By default, it uses the {pkgdown} original template.  
To use your own template, it is better to create a R package with all necessary files (See <https://github.com/tidyverse/tidytemplate> as an example).  

*You can then define your own "_pkgdown.yml" file that will call your template when building the site:  *
```yaml
template:
  package: mypackagetemplate

```

```{r, eval=FALSE}
visualidentity::build_pkgdown(
  lazy = TRUE,
  yml = "/pah/to/your/yaml/_pkgdown.yml",
  favicon = "/path/to/your/favicon.ico",
  move = TRUE
)
```

Help users find your pkgdown website with function `open_pkgdown_function()`. This adds function `open_pkgdown()` inside your package that will open the site on demand.

```{r, eval=FALSE}
visualidentity::open_pkgdown_function()
```

### Build a reference page

To award people hard working for open-source, it is always good to cite their work. In order to add an informative page in your Shiny applications for instance, you can create a html or markdown page listing all package dependencies used. 

```{r, eval=FALSE}
visualidentity::create_pkg_biblio_file(to = "html", out.dir = "inst")
# Can be included in a shiny app using 
shiny::includeHTML("bibliography.html")
# OR
visualidentity::create_pkg_biblio_file(to = "markdown")
# Can be included in a shiny app using 
shiny::includeMarkdown("bibliography.md")
```

## To describe your package and how to install it

This can be useful to create your Readme for instance or to send the instructions file for your clients to install your package.

```{r, eval=FALSE}
path <- system.file("DESCRIPTION", package = "visualidentity")
out.dir <- tempdir()
create_pkg_desc_file(path, source = c("archive"), to = "html")
```

```{r, eval=FALSE}
# Use with results="asis" in a Rmd
shiny::includeHTML(file.path(out.dir, "pkg_description.html"))
```
