---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# visualidentity

The goal of visualidentity is to build package documentation using personnalized templates.

## Installation

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("ThinkR-open/visualidentity")
```


## Examples
### Build a book from vignettes inside a package

You can use `create_book()` using your own template basis. By default, it uses {bookdown} site template. You can use it to build your own.

```{r, eval=FALSE}
template <- system.file("rstudio/templates/project/resources", package = "bookdown")
create_book(path = "inst/report", clean = TRUE,
            template = template)
```

Help users find your book with function `open_guide_function()`. This adds function `open_guide()` inside your package that will open the userguide on demand.

```{r, eval=FALSE}
open_guide_function(path = "inst/report")
```


