---
title: "Create a book from vignettes with bookdown"
author: "Sébastien Rochette"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{01 - Create a book from vignettes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<script type="text/javascript">
$(document).ready(function () {
  window.initializeCodeFolding("show" === "show");
});
</script>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Create book repository inside a package

## Create empty book

Use `create_book` with `clean = TRUE` to remove example Rmd files. You will use your vignettes to fill the book, you do not need example files. Only "index.Rmd" file is kept.

```{r, eval=FALSE}
chameleon::create_book(path = "inst/report", clean = TRUE)
```

- Modify the index page ("index.Rmd") with presentation of the package and/or book.

## Build the book based on vignettes

Function `build_book()` will copy your vignettes in the book directory and build books (html and/or pdf).  

- Vignettes will be incorporated in alpha-numerical order of files names. You may want to name your vignettes starting letters like `aa-vignette-number-one`, `ab-vignette-number-two`. _Note that vignettes names can not start with a number for package build_.
- Each vignette should start with a level 1 title (`# Title 1`) and be followed by titles with lower levels
- Book directory can be cleaned before/after running the book. Only "index.Rmd" and "zzz-references.Rmd" files are kept if exist.

```{r, eval=FALSE}
chameleon::build_book(path = "inst/report", path.v = "vignettes",
            output_format = c("bookdown::gitbook", "bookdown::pdf_book"))
```

## Create short book with index and references only

You may want to send a PDF along with your package archive to targeted people, so that they know what is inside, who developed it, how to install it and where to find the documentation. A short version of the book above, without vignettes.

To do so, you need to fill the index.Rmd file with necessary information and create the book only with index and references.  


## Help user find the userguides

Function `open_guide_function()` adds function `open_guide()` inside your package that will open the userguide on demand.

```{r, eval=FALSE}
chameleon::open_guide_function(path = "inst/report")
```

Users of your package (`pkg`) can now have access to the books using:  

```{r, eval=FALSE}
pkg::open_guide("html")
pkg::open_guide("pdf")
```

Add these in your documentation and/or add a message when loading the package with this function inside your package:

```{r, eval=FALSE}
#' @title .onAttach
#' @noRd
.onAttach <- function(libname, pkgname) {
  message("Read the report with deeptools::open_guide()")
}
```

