---
title: "Create a pkgdown site inside your package"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{02 - Create a pkgdown site}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Create a pkgdown site inside your package

## Create the pkgdown

Use `build_pkgdown` with default option to build the {pkgdown} site and copy it in "inst" so that it is available in your package.

- You can use your own "_pkgdown.yml" with parameter `yml`
- You can use your own favicon with parameter `favicon`

```{r, eval=FALSE}
chameleon::build_pkgdown(
  move = TRUE, clean = TRUE
)
```


## Allow code folding

For code folding to be available in the site, each vignette needs to be initiated with a script. However, {pkgdown} does not use YAML of vignettes to build the site.  
The script below needs to be added as is in the vignette, below the YAML:  

```html
<script type="text/javascript">
$(document).ready(function () {
  window.initializeCodeFolding("show" === "hide");
});
</script> 
```

## Help user find the site

Function `open_pkgdown_function()` adds function `open_pkgdown()` inside your package that will open the userguide on demand.

```{r, eval=FALSE}
chameleon::open_pkgdown_function(path = "docs")
```

Users of your package (`pkg`) can now have access to the site using:  

```{r, eval=FALSE}
pkg::open_pkgdown()
```

Add these in your documentation and/or add a message when loading the package with this function inside your package:

```{r, eval=FALSE}
#' @title .onAttach
#' @noRd
.onAttach <- function(libname, pkgname) {
  message("Open the HTML documentation with deeptools::open_pkgdown()")
}
```
