---
title: "Create a book from vignettes with bookdown"
author: "Sébastien Rochette"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Create a book from vignettes with bookdown}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Create book repository inside a package

Use `create_book` with `clean = TRUE` to remove example Rmd files. You will use your vignettes to fill the book, you do not need example files. Only the "index.Rmd" file is kept.

```{r, eval=FALSE}
create_book(path = "inst/report", clean = TRUE)
```

- Modify the index page with presentation of the book.

# Build the book based on vignettes

Function `build_book()` will copy your vignettes in the book directory and build books (html and/or pdf).

```{r, eval=FALSE}
build_book(path = "inst/report", path.v = "vignettes",
            output_format = c("bookdown::gitbook", "bookdown::pdf_book"))
```

# Help user find the userguides

Function `open_guide_function()` adds function `open_guide()` inside your package that will open the userguide on demand.

```{r}
open_guide_function(path = "inst/report")
```

